Creating figures for the paper

### 2024-08-04 infercnv/reports/paper_figures.Rmd
reorder scripts, trying pdf to help plot.new() issue

# Plot 3 - inferCNV plot with all individuals together

>>>>

# Plot 4 - inferCNV plot with all individuals together

I am currently trying to run this. I have run into some issues with `inferCNV`
dependencies breaking on farm22, so this has been on hold for the last 2 weeks.

# Plot 5 - Mutation hotspots

We load Luke's object. The `nano_muts` are the targeted mutations. The 
`exome_muts` is a list of significant drivers in each cell type (dNdScv output).

```{r}
# add library path
.libPaths(c("/lustre/scratch125/casm/team268im/at31/.R/lib/4.2.2/", .libPaths()))

# libraries
library(GenomicRanges)
library(trackViewer)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)  # package for gene model
library(org.Hs.eg.db)                       # package for gene name

# dirs
lh22_dir <- "/lustre/scratch125/casm/team268im/lh22/Rheumatoid_Arthritis_Paper/"

# load the metadata
sm <- readr::read_tsv(file.path(lh22_dir, "Data/MetaData/sample_meta.tsv"))

# load the muts
load(file.path(lh22_dir, "Figures/Figure_2/LCM_NanoSeq_Overlap/GOI",
               "pileup_muts.rda"))
# muts <- list(exome = exome_muts,
#              LCM = LCM_muts,
#              targeted = nano_muts,
#              pileup = pileup_muts)

# get NF1 mutations, convert to granges

# get mutations, convert to granges
gr_ls <-
  nano_muts %>%
  tibble::as_tibble() %>%
  dplyr::add_count(mut_site) %>%
  {
    GenomicRanges::GRanges(
      seqnames = paste0("chr", .$chr),
      ranges = IRanges::IRanges(start = .$pos,
                                width = 1,
                                names = .$mut_site),
      strand = ifelse(.$strand == 1, "+", "-"),
      gene = .$gene, score = .$n)
  } %>%
  {split(., .$gene)}

# get transcripts in the range
trs <-
  geneModelFromTxdb(TxDb.Hsapiens.UCSC.hg19.knownGene,
                    org.Hs.eg.db, gr = gr_ls$NF1)

entrezID <- get("NF1", org.Hs.egSYMBOL2EG)
theTrack <- geneTrack(entrezID, TxDb.Hsapiens.UCSC.hg19.knownGene)[[1]]
viewerStyle <- trackViewerStyle()
setTrackViewerStyleParam(viewerStyle, "margin", c(.1, .05, .02, .02))
trackList <- trackList(trs)
vp <- viewTracks(trackList,
                 gr = gr, viewerStyle = viewerStyle,
                 autoOptimizeStyle = TRUE)

pdf("test.pdf")
vp
dev.off()

# select transcripts of interest
features <- c(range(trs[[1]]$dat), range(trs[[2]]$dat))
names(features) <- c(trs[[1]]$name, trs[[2]]$name)
features$fill <- c("lightblue", "mistyrose")

# lollipop
pdf("test.pdf", width = 30)
lolliplot(gr_ls$NF1, features,
          ranges = GRanges("chr17", IRanges(29421945, 29704695, names = "NF1")), 
          type = "circle")
dev.off()

# get genes from biomart
txdb <- TxDb.Hsapiens.UCSC.hg19.knownGene
broads <- GenomicFeatures::genes(txdb)
seqlevels(broads) <- gsub("chr", "", seqlevels(broads))

# get gene annotations from broads
feats <- broads[seqnames(broads) %in% seqlevels(gr)]
findOverlaps(gr, broads)

feats <-
  GenomicRanges::GRanges("12", IRanges::IRanges(start = 6702320, end = 6702330),
                         strand = "+", gene = "NF1")

trackViewer::lolliplot(SNP.gr = head(gr, 1), features = feats)
```
